---
title: "Case Study"
output: github_document
---

```{r setup}
library(tidyverse)
library(patchwork)
library(p8105.datasets)
```

## Load the airbnb data

```{r}
data("nyc_airbnb")
```

## Brainstorm some questions
(Technical problem)
```{r}
nyc_airbnb %>% slice(1:1000)
nyc_airbnb %>% sample_n(1000)
nyc_airbnb %>% sample_frac(size = .1)
```
What is the best Staten island < $100?
What price range is popular each borough? most rented?
What apartment features are related to price?
Cheapest room type in each neighborhood?
Host have higher ratings?

##

```{r}
nyc_airbnb %>% 
  filter(neighbourhood_group == "Staten Island" & price < 100) %>%
  arrange(desc(review_scores_location))
```
data cleaning
```{r}
nyc_airbnb <- nyc_airbnb %>%
  mutate(stars = review_scores_location / 2)
  
```
```{r}
nyc_airbnb %>% 
  count(neighbourhood_group, room_type) %>% 
  pivot_wider(names_from = room_type, values_from = n)
```
```{r}
nyc_airbnb %>% 
  group_by(neighbourhood_group, room_type) %>% 
  summarise(mean_price = mean(price))
```
```{r}
nyc_airbnb %>% 
  filter(neighbourhood_group == "Manhattan") %>% 
  count(neighbourhood)

nyc_airbnb %>% 
  filter(price < 1000, neighbourhood_group == "Manhattan") %>% 
  mutate(neighbourhood = fct_reorder(neighbourhood, price)) %>% 
  ggplot(aes(x = neighbourhood, y = price)) + 
  geom_boxplot() +
  coord_flip()
```
```{r}
nyc_airbnb %>% 
  sample_n(1000) %>% 
  ggplot(aes(x = lat , y = long, color = price))+
  geom_point()
```
## Leaflet
```{r}
pal <- leaflet::colorNumeric("viridis", nyc_airbnb %>% pull(stars))

nyc_airbnb %>% 
  sample_n(5000) %>% 
  leaflet::leaflet() %>% 
  leaflet::addTiles() %>% 
  leaflet::addCircleMarkers(~lat, ~long, radius = 1, color = ~ pal(stars))
```


